JD notes on effects

### 2022-03-13 manuscript/jd_notes.Rmd

The lines inside (effects) are a little different: they are a good way to visualize the effect of the focal predictor. Unlike predictions, where the uncertainty captures the uncertainty in the whole model, the effects plot focuses on uncertainty in the effect of the focal predictor only -- thus, for example, if an effect is barely significant (P exactly 0.05), one end of the CI will be exactly a straight line for the effects plot, but not for the prediction plot. Also, the uncertainty curves for the effect, but not for the prediction, depend on the "anchor".

>>>>

The lines inside (effects) are a little different: they are a good way to visualize the effect of the focal predictor. Unlike predictions, where the uncertainty captures the uncertainty in the whole model, the effects plot focuses on uncertainty in the effect of the focal predictor only -- thus, for example, if an effect is barely significant (P exactly 0.05), one end of the CI will be exactly a horizontal line for the effects plot, but not for the prediction plot. Also, the uncertainty curves for the effect, but not for the prediction, depend on the "anchor".
